---
title: "Results"
author: "Maria Kuruvilla"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results

### Coho

```{r packages}
#packages
library(here)
library(MARSS)
library(tidyverse)
library(ggplot2)
library(zoo)


```


```{r data}


data <- read.csv(here("data","dungeness_subset_covariates.csv"), header = TRUE)

data$coho1_hatchery_num_interpolate <- na.approx(data$coho1_hatchery_num)



```


```{r wrangling_data}


subset <- arrange(data,doy) %>%
  filter(year != 2015 & doy > 100 & doy <= 185) %>%
  mutate(log.value = ifelse(coho1_wild_num == 0, NA, log(coho1_wild_num))) %>%
  select(log.value,year,doy) %>%
  pivot_wider(names_from = year, values_from = log.value) %>%
  column_to_rownames(var = "doy") %>%
  as.matrix() %>%
  t()

#scale the values

for(i in 1:dim(subset)[1]){
  subset[i,] = scale(subset[i,])[,1]
}

covariates_all_years <- arrange(data,doy) %>%
  filter(year != 2015 & doy >100 & doy <= 185) %>%
  select(year,doy, temp, atu_april, photoperiod, flow, coho1_hatchery_num_interpolate) %>%
  pivot_wider(names_from = year, values_from = c(
    temp, atu_april, photoperiod, flow, coho1_hatchery_num_interpolate)) %>%
  column_to_rownames(var = "doy") %>%
  as.matrix() %>%
  t()

for(i in 1:(dim(covariates_all_years)[1]-15)){
  covariates_all_years[i,] = scale(covariates_all_years[i,])[,1]
}


```


```{r model_structure}

mod.list0 <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and unequal",
  C = "zero"
)

mod.list <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and unequal",
  C = "diagonal and unequal"
)

#putting it into a loop

c.models <- list( 
  c1 = "zero", # No covariates
  c2 = covariates_all_years[1:15,], # Temperature
  c3 = covariates_all_years[16:30,], # ATU April
  c4 = covariates_all_years[31:45,],  #Photoperiod
  c5 = covariates_all_years[46:60,],  #Flow
  c6 = covariates_all_years[61:75,]  #Hatchery
)
names(c.models) <- c("No covariates", "Temperature", "ATU", "Photoperiod", "Flow", "Hatchery")

```

```{r model_fit_loop, cache = TRUE}


out.tab <- NULL
fits <- list()
for(i in 1:length(c.models)){
  if(i == 1){
    fit.model = c(list(c= c.models[[i]]), mod.list0)
  }
  else{
    fit.model = c(list(c= c.models[[i]]), mod.list)
  }
  
  fit <- MARSS(subset, model=fit.model, silent = TRUE,
                   control=list(maxit=2000, allow.degen=TRUE))

      
      out=data.frame(c=names(c.models)[i], 
                     logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                     num.iter=fit$numIter, converged=!fit$convergence,
                     stringsAsFactors = FALSE)
      out.tab=rbind(out.tab,out)
      fits=c(fits,list(fit))
      
}

 

min.AICc <- order(out.tab$AICc)
out.tab.1 <- out.tab[min.AICc, ]
out.tab.1



```



Trying combination of variables

```{r model_structure_two_variables}

mod.list <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and unequal",
  C = matrix(list("p2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"p2006",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2006",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"p2007",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2007",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"p2008",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2008",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"p2009",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2009",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"p2010",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2010",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"p2011",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2011",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"p2012",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2012",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"p2013",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2013",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"p2014",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2014",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"p2016",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2016",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"p2017",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2017",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"p2018",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2018",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"p2019",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2019",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p2020",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2020"),
             15,30, byrow = TRUE)
)

#putting it into a loop

c.models <- list( 
  c2 = covariates_all_years[c(1:15,46:60),], # Temperature
  c3 = covariates_all_years[c(16:30,46:60),], # ATU April
  c4 = covariates_all_years[c(31:45,46:60),],  #Photoperiod
  c6 = covariates_all_years[c(61:75,46:60),]  #Hatchery
)
names(c.models) <- c("Temperature and Flow", "ATU and Flow", "Photoperiod and Flow", " Hatchery and Flow")



```


```{r model_fit_two_variables, cache = TRUE}



out.tab2 <- NULL
fits <- list()
for(i in 1:length(c.models)){
  fit.model = c(list(c= c.models[[i]]), mod.list)
  fit <- MARSS(subset, model=fit.model, silent = TRUE,
                   control=list(maxit=2000, allow.degen=TRUE))

      
      out=data.frame(c=names(c.models)[i], 
                     logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                     num.iter=fit$numIter, converged=!fit$convergence,
                     stringsAsFactors = FALSE)
      out.tab2=rbind(out.tab2,out)
      fits=c(fits,list(fit))
      
}

 

min.AICc <- order(out.tab2$AICc)
out.tab.2 <- out.tab2[min.AICc, ]
out.tab.2




```


Adding flow to the observational covariate:

```{r obs_cov}

mod.list0.d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and unequal",
  C = "zero",
  D = "diagonal and unequal",
  d = covariates_all_years[46:60,]
)


mod.list.d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and unequal",
  C = "diagonal and unequal",
  D = "diagonal and unequal",
  d = covariates_all_years[46:60,]
)

c.models <- list( 
  c1 = "zero", # No covariates
  c2 = covariates_all_years[1:15,], # Temperature
  c3 = covariates_all_years[16:30,], # ATU April
  c4 = covariates_all_years[31:45,],  #Photoperiod
  c5 = covariates_all_years[46:60,],  #Flow
  c6 = covariates_all_years[61:75,]  #Hatchery
)
names(c.models) <- c("No covariates", "Temperature", "ATU", "Photoperiod", "Flow", "Hatchery")


```


```{r model_fit_obs_variables, cache = TRUE}



out.tab3 <- NULL
fits <- list()
for(i in 1:length(c.models)){
  if(i == 1){
    fit.model = c(list(c= c.models[[i]]), mod.list0.d)
  }
  else{
    fit.model = c(list(c= c.models[[i]]), mod.list.d)
  }
  
  fit <- MARSS(subset, model=fit.model, silent = TRUE,
                   control=list(maxit=2000, allow.degen=TRUE))

      
      out=data.frame(c=names(c.models)[i], d="Flow",
                     logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                     num.iter=fit$numIter, converged=!fit$convergence,
                     stringsAsFactors = FALSE)
      out.tab3=rbind(out.tab3,out)
      fits=c(fits,list(fit))
      
}

 

min.AICc <- order(out.tab3$AICc)
out.tab.3 <- out.tab3[min.AICc, ]
out.tab.3




```


Adding flow to both observational and state covariates:


```{r obs_state_cov}



mod.list.d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and unequal",
  C = matrix(list("p2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"p2006",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2006",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"p2007",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2007",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"p2008",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2008",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"p2009",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2009",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"p2010",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2010",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"p2011",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2011",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"p2012",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2012",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"p2013",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2013",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"p2014",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2014",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"p2016",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2016",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"p2017",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2017",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"p2018",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2018",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"p2019",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2019",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p2020",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2020"),
             15,30, byrow = TRUE),
  D = "diagonal and unequal",
  d = covariates_all_years[46:60,]
)

c.models <- list( 
  c2 = covariates_all_years[c(1:15,46:60),], # Temperature
  c3 = covariates_all_years[c(16:30,46:60),], # ATU April
  c4 = covariates_all_years[c(31:45,46:60),],  #Photoperiod
  c5 = covariates_all_years[c(61:75,46:60),]  #Hatchery
)
names(c.models) <- c("Temperature and Flow", "ATU and Flow", "Photoperiod and Flow", "Hatchery and Flow")


```




```{r model_fit_obs_state_variables, cache = TRUE}



out.tab4 <- NULL
fits <- list()
for(i in 1:length(c.models)){
  fit.model = c(list(c= c.models[[i]]), mod.list.d)
  fit <- MARSS(subset, model=fit.model, silent = TRUE,
                   control=list(maxit=4000, allow.degen=TRUE))

      
      out=data.frame(c=names(c.models)[i], d="Flow",
                     logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                     num.iter=fit$numIter, converged=!fit$convergence,
                     stringsAsFactors = FALSE)
      out.tab4=rbind(out.tab4,out)
      fits=c(fits,list(fit))
      
}

 

min.AICc <- order(out.tab4$AICc)
out.tab.4 <- out.tab4[min.AICc, ]
out.tab.4




```


Trying Photoperiod, Flow and Hatchery in the state covariates and  Flow in the observation covarates:



```{r include_hatchery. cache = TRUE}
mod.list.d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and unequal",
  C = matrix(list("p2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"p2006",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2006",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2006",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"p2007",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2007",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2007",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"p2008",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2008",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2008",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"p2009",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2009",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2009",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"p2010",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2010",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2010",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"p2011",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2011",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2011",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"p2012",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2012",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2012",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"p2013",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2013",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2013",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"p2014",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2014",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2014",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"p2016",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2016",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2016",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"p2017",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2017",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2017",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"p2018",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2018",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2018",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"p2019",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2019",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2019",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p2020",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2020",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2020"),
             15,45, byrow = TRUE),
  D = "diagonal and unequal",
  d = covariates_all_years[46:60,]
)

c.models <- list( 
  c2 = covariates_all_years[c(31:45,61:75,46:60),] # photoperiod, hatchery. flow

)
names(c.models) <- c("Photoperiod, Hatchery, and Flow")


```



```{r model_fit_hatchery, cache = TRUE}



out.tab5 <- NULL
fits5 <- list()
for(i in 1:length(c.models)){
  fit5.model = c(list(c= c.models[[i]]), mod.list.d)
  fit5 <- MARSS(subset, model=fit5.model, silent = TRUE,
                   control=list(maxit=4000, allow.degen=TRUE))

      
      out=data.frame(c=names(c.models)[i], d="Flow",
                     logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                     num.iter=fit$numIter, converged=!fit$convergence,
                     stringsAsFactors = FALSE)
      out.tab5=rbind(out.tab5,out)
      fits5=c(fits5,list(fit5))
      
}

 

min.AICc <- order(out.tab5$AICc)
out.tab.5 <- out.tab5[min.AICc, ]
out.tab.5




```


```{r}
autoplot(fits[[3]])
```


Let's try photoperiod, flow in the state covariates, flow in the observational covariates, and the same process error for all years


```{r same_process_error}



mod.list.d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = matrix(list("p2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"p2006",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2006",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"p2007",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2007",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"p2008",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2008",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"p2009",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2009",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"p2010",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2010",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"p2011",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2011",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"p2012",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2012",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"p2013",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2013",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"p2014",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2014",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"p2016",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2016",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"p2017",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2017",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"p2018",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2018",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"p2019",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2019",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p2020",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f2020"),
             15,30, byrow = TRUE),
  D = "diagonal and unequal",
  d = covariates_all_years[46:60,]
)

c.models <- list( 
  
  c4 = covariates_all_years[c(31:45,46:60),] #Photoperiod
  
)
names(c.models) <- c("Photoperiod and Flow")


```


```{r model_fit_same_process_error, cache = TRUE}



out.tab6 <- NULL
fits6 <- list()
for(i in 1:length(c.models)){
  fit.model = c(list(c= c.models[[i]]), mod.list.d)
  fit6 <- MARSS(subset, model=fit.model, silent = TRUE,
                   control=list(maxit=4000, allow.degen=TRUE))

      
      out=data.frame(c=names(c.models)[i], d="Flow",
                     logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                     num.iter=fit$numIter, converged=!fit$convergence,
                     stringsAsFactors = FALSE)
      out.tab6=rbind(out.tab6,out)
      fits6=c(fits6,list(fit6))
      
}

 

min.AICc <- order(out.tab6$AICc)
out.tab.6 <- out.tab6[min.AICc, ]
out.tab.6




```


```{r}
autoplot(fits6[[1]])
```

```{r, cache = TRUE}
kem.with.CIs.from.hessian <- MARSSparamCIs(fits6[[1]], nboot = 1000)
```





```{r}
library(broom)
ci <- tidy(fits6[[1]])


```


```{r}

# Plot parameter estimates and confidence intervals
ggplot(ci[33:62,], aes(x = term, y = estimate, ymin = conf.low, ymax = conf.up)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Parameter", y = "Estimate") +
  ggtitle("Parameter Estimates with Confidence Intervals")

```



Trying model with just hatchery variables

```{r}
mod.list.h <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = "diagonal and unequal",
  c = covariates_all_years[61:75,]
)
fit.h <- MARSS(subset, model=mod.list.h, silent = TRUE,
                   control=list(maxit=2000, allow.degen=TRUE))


```



```{r}
fit.h$AICc
autoplot(fit.h)
```


```{r}
ci <- tidy(fit.h)

```


```{r}
ggplot(ci[18:32,], aes(x = term, y = estimate, ymin = conf.low, ymax = conf.up)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Parameter", y = "Estimate") +
  ggtitle("Parameter Estimates with Confidence Intervals")


```

Now adding other covariates


```{r}
mod.list_all <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = matrix(list("p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2006",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2007",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2008",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2009",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2010",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2011",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2012",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2013",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2014",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2016",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2017",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2018",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2019",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"f",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2020"),
             15,45, byrow = TRUE),
  c = covariates_all_years[c(31:45,46:75),],
  D = "diagonal and unequal",
  d = covariates_all_years[46:60,]
)
fit_all <- MARSS(subset, model=mod.list_all, silent = TRUE,
                   control=list(maxit=2000, allow.degen=TRUE))
```

```{r}
fit_all$AICc

```

```{r}
ci_all <- tidy(fit_all)
```

```{r}
ggplot(ci_all[35:49,], aes(x = term, y = estimate, ymin = conf.low, ymax = conf.up)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Parameter", y = "Estimate") +
  ggtitle("Parameter Estimates with Confidence Intervals")


```
