---
title: "Results"
author: "Maria Kuruvilla"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results

### Coho

```{r packages}
#packages
library(here)
library(MARSS)
library(tidyverse)
library(ggplot2)
library(zoo)
library(broom)
library(ggfortify)

```


```{r data}


data <- read.csv(here("data","dungeness_subset_covariates.csv"), header = TRUE)

data$coho1_hatchery_num_interpolate <- na.approx(data$coho1_hatchery_num)



```


```{r wrangling_data}


subset <- arrange(data,doy) %>%
  filter(year != 2015 & doy > 100 & doy <= 185) %>%
  mutate(log.value = ifelse(coho1_wild_num == 0, NA, log(coho1_wild_num))) %>%
  select(log.value,year,doy) %>%
  pivot_wider(names_from = year, values_from = log.value) %>%
  column_to_rownames(var = "doy") %>%
  as.matrix() %>%
  t()

#scale the values

for(i in 1:dim(subset)[1]){
  subset[i,] = scale(subset[i,])[,1]
}

covariates_all_years <- arrange(data,doy) %>%
  filter(year != 2015 & doy >100 & doy <= 185) %>%
  select(year,doy, temp, atu_april, photoperiod, flow, lunar_phase, coho1_hatchery_num_interpolate) %>%
  pivot_wider(names_from = year, values_from = c(
    temp, atu_april, photoperiod, flow, lunar_phase, coho1_hatchery_num_interpolate)) %>%
  column_to_rownames(var = "doy") %>%
  as.matrix() %>%
  t()

for(i in 1:(dim(covariates_all_years)[1]-15)){
  covariates_all_years[i,] = scale(covariates_all_years[i,])[,1]
}


```


```{r model_structure}

mod.list_base <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal"
)

mod.list_d_base <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  D = "diagonal and equal",
  d = covariates_all_years[46:60,] 
)


mod.list_equal <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = "diagonal and equal"
)

mod.list_d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = "diagonal and equal",
  D = "diagonal and equal",
  d = covariates_all_years[46:60,] 
)


#putting it into a loop

c.models <- list( 
  c1 = "zero", # No covariates
  c2 = covariates_all_years[1:15,], # Temperature
  c3 = covariates_all_years[16:30,], # ATU April
  c4 = covariates_all_years[31:45,],  #Photoperiod
  c5 = covariates_all_years[46:60,],  #Flow
  c6 = covariates_all_years[61:75,],  #Lunar phase
  c7 = covariates_all_years[76:90,]  #Hatchery
)
names(c.models) <- c("No covariates", "Temperature", "ATU", "Photoperiod", "Flow", "Lunar Phase", "Hatchery")



```


```{r model_fit_loop, cache = TRUE}


out.tab <- NULL
fits <- list()
for(i in 1:length(c.models)){
  
    
    if(names(c.models)[i] == "No covariates"){
      
      fit.model = mod.list_base
    }
      
    else{
      fit.model = c(list(c= c.models[[i]]), mod.list_equal)
        
    }
    

    fit <- MARSS(subset, model=fit.model, silent = TRUE, method = "BFGS",
                 control=list(maxit=2000))


    out=data.frame(c=names(c.models)[i], d="No covariates",
                   logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                   num.iter=fit$numIter, converged=!fit$convergence,
                   stringsAsFactors = FALSE)
    out.tab=rbind(out.tab,out)
    fits=c(fits,list(fit))
  
      
}



min.AICc <- order(out.tab$AICc)
out.tab.1 <- out.tab[min.AICc, ]
out.tab.1



```

Since the model with photoperiod has lower AIC than the model with ATU and the model with temperature, I will only keep photoperiod in the subsequent models. 



```{r mult_models, cache = TRUE}

c.models <- list( 
  
  
  c2 = covariates_all_years[c(46:60,31:45),],  #Flow and photoperiod
  c3 = covariates_all_years[c(61:75,31:45),],  #Lunar phase and photoperiod
  c4 = covariates_all_years[c(46:60,61:75,31:45),]  #flow, Lunar phase and photoperiod
)
names(c.models) <- c("Flow, Photoperiod", "Lunar Phase, Photoperiod", "Flow, Lunar Phase, Photoperiod")

mod.list_equal <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = matrix(list("a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p"),
             15,30, byrow = TRUE)
)


mod.list_equal3 <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = matrix(list("a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,"p"),
             15,45, byrow = TRUE)
)




```


```{r model_fit_loop3, cache = TRUE}


out.tab3 <- NULL
fits3 <- list()
for(i in 1:length(c.models)){
  
    
    if(names(c.models)[i] == "Flow, Lunar Phase, Photoperiod"){
      
      fit.model = c(list(c= c.models[[i]]), mod.list_equal3)
    }
      
    else{
      fit.model = c(list(c= c.models[[i]]), mod.list_equal)
        
    }
    

    fit <- MARSS(subset, model=fit.model, silent = TRUE, method = "BFGS",
                 control=list(maxit=2000))


    out=data.frame(c=names(c.models)[i], d="No covariates",
                   logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                   num.iter=fit$numIter, converged=!fit$convergence,
                   stringsAsFactors = FALSE)
    out.tab3=rbind(out.tab3,out)
    fits3=c(fits3,list(fit))
  
      
}



min.AICc <- order(out.tab3$AICc)
out.tab.3 <- out.tab3[min.AICc, ]
out.tab.3



```


Now adding flow to the d covariates

```{r}


c.models <- list( 
  
  
  c2 = covariates_all_years[c(46:60,31:45),],  #Flow and photoperiod
  c3 = covariates_all_years[c(61:75,31:45),],  #Lunar phase and photoperiod
  c4 = covariates_all_years[c(46:60,61:75,31:45),]  #flow, Lunar phase and photoperiod
)
names(c.models) <- c("Flow, Photoperiod", "Lunar Phase, Photoperiod", "Flow, Lunar Phase, Photoperiod")

mod.list_equal1_d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = "diagonal and equal",
  D = "diagonal and equal",
  d = covariates_all_years[46:60,]
)

mod.list_equal_d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = matrix(list("a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p"),
             15,30, byrow = TRUE),
  D = "diagonal and equal",
  d = covariates_all_years[46:60,]
)


mod.list_equal3_d <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = matrix(list("a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"p",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,"p"),
             15,45, byrow = TRUE),
  D = "diagonal and equal",
  d = covariates_all_years[46:60,]
)






```




```{r model_fit_loop3_d, cache = TRUE}


out.tab3_d <- NULL
fits3_d <- list()
for(i in 1:length(c.models)){
  if(names(c.models)[i] == "Photoperiod"){
    
    print(i)
    fit.model = c(list(c= c.models[[i]]), mod.list_equal1_d)
    }
  if(names(c.models)[i] == "Flow, Lunar Phase, Photoperiod"){
    
      
    fit.model = c(list(c= c.models[[i]]), mod.list_equal3_d)
    }
  else{
    fit.model = c(list(c= c.models[[i]]), mod.list_equal_d)
        
    }
  fit <- MARSS(subset, model=fit.model, silent = TRUE, method = "BFGS",
                 control=list(maxit=2000))


  out=data.frame(c=names(c.models)[i], d="Flow",
                   logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                   num.iter=fit$numIter, converged=!fit$convergence,
                   stringsAsFactors = FALSE)
  out.tab3_d=rbind(out.tab3_d,out)
  fits3_d=c(fits3_d,list(fit))
  
      
}



min.AICc <- order(out.tab3_d$AICc)
out.tab.3_d <- out.tab3_d[min.AICc, ]
out.tab.3_d



```


Model with Flow, Lunar phase and Photoperiod in the process covariates has the lowest AICc. Now I am adding unequal hatchery for every year.


```{r unequal_hatchery, cache = TRUE}

c.models <- list( 
  
  
  c4 = covariates_all_years[c(46:60,31:45,61:75,76:90),]  #flow, photoperiod, lunar phase and hatchery
)
names(c.models) <- c("Flow, Photoperiod, Lunar Phase, Hatchery")



mod.list_unequal_h <- list(
  U = "zero",
  R = "diagonal and equal",
  Q = "diagonal and equal",
  C = matrix(list("a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2005",0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2006",0,0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2007",0,0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2008",0,0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2009",0,0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2010",0,0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2011",0,0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2012",0,0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2013",0,0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2014",0,0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2016",0,0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2017",0,0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2018",0,0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2019",0,
                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,"a",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"b",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"c",0,0,0,0,0,0,0,0,0,0,0,0,0,0,"h2020"),
             15,60, byrow = TRUE)
)




```




```{r model_fit_loop3_d, cache = TRUE}


out.tabh_d <- NULL
fitsh_d <- list()
for(i in 1:length(c.models)){
  
    
    
    fit.model = c(list(c= c.models[[i]]), mod.list_unequal_h)
        
    
    

    fit <- MARSS(subset, model=fit.model, silent = TRUE, method = "BFGS",
                 control=list(maxit=2000))


    out=data.frame(c=names(c.models)[i], d="No covariates",
                   logLik=fit$logLik, AICc=fit$AICc, num.param=fit$num.params,
                   num.iter=fit$numIter, converged=!fit$convergence,
                   stringsAsFactors = FALSE)
    out.tabh_d=rbind(out.tabh_d,out)
    fitsh_d=c(fitsh_d,list(fit))
  
      
}



min.AICc <- order(out.tabh_d$AICc)
out.tab.h_d <- out.tabh_d[min.AICc, ]
out.tab.h_d



```

```{r}
ci <- tidy(fitsh_d[[1]])
year = 2005
for(i in 21:35){
  if(year == 2015){
    year = year + 1
  }
  ci[i,1] = toString(year)
  
  year = year + 1
}
print(ci)
```

Plotting environmental covariates

```{r}
ggplot(ci[18:20,], aes(x = c("Flow","Photoperiod", "Lunar phase"), y = estimate, ymin = conf.low, ymax = conf.up)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "", y = "Estimate of environmental effect") +
  ggtitle("Environmental effects") + 
    theme(plot.title = element_text(size = 20))+
  theme(axis.text.x=element_text(size=14),axis.title.y=element_text(size=14))

ggsave(here("output","environmental_effect.jpeg"), width = 10, height = 8)
```



```{r}
ggplot(ci[21:35,], aes(x = term, y = estimate, ymin = conf.low, ymax = conf.up)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Year", y = "Estimate of Hatchery effect") +
  ggtitle("Effect of hatchery Coho") + 
    theme(plot.title = element_text(size = 20))+
  theme(axis.title.x=element_text(size=14),axis.title.y=element_text(size=14))
  
ggsave(here("output","hatchery_effect.jpeg"), width = 10, height = 8)
```
```{r}
out.tab.final <- as.data.frame(rbind(out.tab.1,rbind(out.tab.3, out.tab.3_d)))
out.tab.final$DeltaAICc = out.tab.final$AICc - min(out.tab.final$AICc)
out.tab.final <- out.tab.final[order(out.tab.final$AICc),]
row.names(out.tab.final) <- NULL
write.csv(out.tab.final,file = here("output","coho_tab.csv"))
print(out.tab.final)
```

```{r}
autoplot(fitsh_d[[1]], plot.type = "fitted.ytT")
ggsave(here("output","fitted_y_coho.jpeg"), width = 10, height = 8)


```

